data_collation

### 2024-04-12 scripts/data_collation.Rmd
cleaning up data

# Combine kelp dataframes
```{r}

@@

@@

# use rbind.fill() method in R to combine data frames with different columns
fish_data <- rbind.fill(FtWeatherill_fish_2016, FtWeatherill_fish_2017, fish_2018_Hump_Lab_size_classes, fish, fish_Aggregated)

@@

# fish dataframe has size in wide format, discuss I can change this to long is you want but wanted to make sure size classes matched

@@

@@

# the one QUAD data.frame has 130 variables because each species is listed instead of its code, fo you want me to replace with the code and make it wide to long format?

>>>>

# Combine kelp dataframes
```{r}
# Kelp data is cleaned and ready

@@

# Morph data is cleaned and ready

@@

# use rbind.fill() method in R to combine data frames with different columns
fish_data <- rbind.fill(FtWeatherill_fish_2016, FtWeatherill_fish_2017, fish_2018_Hump_Lab_size_classes)

@@

# look at fish_Aggregated later, this is kelp density possibly?

@@

# To do: species codes transform

@@
